The Mysterious Lives Of Speckles. I. Residual atmospheric speckle lifetimes in ground-based coronagraphs

### 2021-05-24 response.txt

Response: in both Figures 2 and 7 we have changed the text to read "The same colorbar is used for both calculated and simulated within a combination of controller and guidestar, but is adjusted to best show detail for each combination"
----------------------------------------------

Figure 8
Comment: Why do the calculations under-predict the speckle lifetimes at separations greater
than 10L/D for the infinitely bright, LP case?

Response: To address this, we have added additional text at the end of Section 5.4:
"The calculated and simulated lifetimes agree throughout most of the control region.  The noteworthy exception occurs in the LP roughly along a diagonal.  At wider separations the simulations predict lifetimes $\sim 50\%$ higher in a wedged shape region.  As with the differences in the phase dynamics discussed above, we attribute this to differences between the orthogonalized modal basis used in the simulations and the Fourier modes used in the calculations, and the resultant changes in the output of the controller coefficients and gain optimization."

And to the caption of Figure 8 we added: "The large difference in median lifetime between simulation and calculation for the
LP on the bright star is due to the wedge shaped region where the simulation predicts higher lifetimes (see Figure 7, and text for discussion)"

@@

Response:  We have added additional explanatory text.  The paragraph introducing the parameter analysis was re-worded to say:

"Note that the input power per Fourier mode scales as $D^{-2}$, that is it will be lower given larger $D$.  This means that the input temporal PSD has a different shape due to relative spatial frequency as well as different power due both to the wind speed and diameter. The input noise PSD will also be lower for each mode, but by $D^{-1}$ since the signal to noise ratio goes as S/N $\propto \sqrt{D}$.  The balance betwen these inputs can be expected to affect the performance of the optimized controllers, resulting in variation in speckle lifetimes."

The paragraph about r_0 now says:

"For the SI controller, improving seeing (larger $r_0$) reduces speckle lifetime.  As the turbulence power is reduced, the control system is better able to reject low temporal frequencies, resulting in lower speckle lifetimes.  As with $D$ and $\mathcal{V}$, the LP controller shows little variation in lifetimes vs. $r_0$.  Here again, the predictive controller whitens the noise to the same floor set by photon noise, which produces an output PSD of roughly the same shape resulting in similar speckle lifetimes.  The lifetime increases somewhat vs $r_0$ on the larger diameters as the turbulence power becomes relatively lower compared to photon noise, resulting in reduced effectiveness of the predictor such that more correlations remain in the output."

### 2021-05-24 specklelives.tex
update

\begin{figure}
\hspace{-0.3in}
\includegraphics[width=6.5in]{lifetimesRP.pdf}
\caption{Median radial profiles of the lifetime maps shown in Figure \ref{fig:lifetime_2Dcomp}.  Left: without photon noise, considering the input turbulence only.  Right: with photon noise on an 8th mag star assuming the sensitivity of an unmodulated pyramid WFS. Speckle lifetime is shorter under predictive control compared to the simple integrator. \textbf{The large difference in median lifetime between simulation and calculation for the LP is due to the wedge shaped region where the simulation predicts higher lifetimes (see Figure \ref{fig:lifetime_2Dcomp}.  See text for discussion.}  \label{fig:lifetime_radprof}}
\end{figure}

>>>>

\begin{figure}
\hspace{-0.3in}
\includegraphics[width=6.5in]{lifetimesRP.pdf}
\caption{Median radial profiles of the lifetime maps shown in Figure \ref{fig:lifetime_2Dcomp}.  Left: without photon noise, considering the input turbulence only.  Right: with photon noise on an 8th mag star assuming the sensitivity of an unmodulated pyramid WFS. Speckle lifetime is shorter under predictive control compared to the simple integrator. \textbf{The large difference in median lifetime between simulation and calculation for the LP on the bright star is due to the wedge shaped region where the simulation predicts higher lifetimes (see Figure \ref{fig:lifetime_2Dcomp}, and text for discussion).}  \label{fig:lifetime_radprof}}
\end{figure}
